Optimizing Monocular Depth Estimation with Global Depth Histogram Matching using a Single SPAD

### 2019-10-07 paper/cvpr2020/sections/method.tex
Added pseudocode for exact histogram matching.

@@

\paragraph{Exact Histogram Matching}
\begin{figure}
  \includegraphics[width=\textwidth/2]{full_pipeline.jpeg}
  \caption{\textbf{Overview of the full pipeline} We use a CNN to get an initial
  per-pixel depth estimate. Then we perform exact histogram matching using
  intensity-weighted pixel values on the corrected SPAD data.}
\end{figure}
An image's \textit{histogram} is a pair of vectors $(h, b)$ where $h_i$ is the number of
pixels of the image whose value lies in the range $[b_i, b_i+1)$.
Then, given a source image $S$ with histogram $(h_s, b)$ and a target histogram
$(h_t, b)$, histogram matching generates a new image $M$ such that $h_m \approx
h_t$ and the pixel values in $M$ are in the same relative order as in $S$.
The full details of the exact histogram matching algorithm can be found in
\cite{Morovic2002}.

@@

\paragraph{SPAD Denoising}
\begin{itemize}
  \item Talk about histogram matching in the ideal case, jump straight to intensity 
  \item Talk about histogram matching in our case, and how it approaches the
    ideal case. Discuss the following corrections 
    \begin{itemize}
      \item Ambient/DC - Use \cite{Xin2019} to justify looking for large edges,
        then the ambient estimate to get rid of the noise floor.
      \item Falloff
    \end{itemize}
  \item Talk about how the histogram matching works with intensity
    considerations applied, briefly.
  \item We don't address jitter or poisson noise.
\end{itemize}
\begin{equation}
  h[n] \sim \mathcal{P}\paren*{\sum_{x,y}\alpha_{x,y}\eta \lambda_{x,y}[n] + b} \label{global_hints}
\end{equation}
Given a SPAD with histogram $h$ according to the above equation, we first
process the SPAD to remove the effects of some of the terms. First, we 
\subsection{Implementation Details}
For the Monocular Depth Estimator, we use pretrained versions of the
the Deep Ordinal Regression Network (DORN) \cite{} and the DenseDepth Network.
The exact histogram matching method is as described in \cite{}.

>>>>

\paragraph{SPAD Denoising}
\begin{itemize}
  \item Talk about histogram matching in the ideal case, jump straight to intensity 
  \item Talk about histogram matching in our case, and how it approaches the
    ideal case. Discuss the following corrections 
    \begin{itemize}
      \item Ambient/DC - Use \cite{Xin2019} to justify looking for large edges,
        then the ambient estimate to get rid of the noise floor.
      \item Falloff
    \end{itemize}
  \item Talk about how the histogram matching works with intensity
    considerations applied, briefly.
  \item We don't address jitter or poisson noise.
\end{itemize}
\begin{equation}
  h[n] \sim \mathcal{P}\paren*{\sum_{x,y}\alpha_{x,y}\eta \lambda_{x,y}[n] + b} \label{global_hints}
\end{equation}
Given a SPAD with histogram $h$ according to the above equation, we first
process the SPAD to remove the effects of some of the terms. First, we

@@

\paragraph{Exact Histogram Matching}
\begin{figure*}
  \centering
  \includegraphics[height=2.5in]{full_pipeline.jpeg}
  \caption{\textbf{Overview of the full pipeline} We use a CNN to get an initial
  per-pixel depth estimate. Then we perform exact histogram matching using
  intensity-weighted pixel values on the corrected SPAD data.}
\end{figure*}
An image's \textit{histogram} is a pair of vectors $(h, b)$ where $h_i$ is the number of
pixels of the image whose value lies in the range $[b_i, b_i+1)$.
Then, given a source image $S$ with histogram $(h_s, b)$ and a target histogram
$(h_t, b)$, histogram matching generates a new image $M$ such that $h_m \approx
h_t$ and the pixel values in $M$ are in the same relative order as in $S$.
The full details of the exact histogram matching algorithm can be found in
\cite{Morovic2002}.

\begin{algorithm}[H]
 \caption{Exact Histogram Matching} 
 \label{alg:ehm}
 \input{sections/figures/exact_hist_matching_pseudo.tex}
\end{algorithm}

@@

\subsection{Implementation Details}
For the Monocular Depth Estimator, we use pretrained versions of the
the Deep Ordinal Regression Network (DORN) \cite{} and the DenseDepth Network.
The exact histogram matching method is as described in \cite{}.
